---
title: "Supplement: Data Analyses for Manuscript"
author: "Debbie Yee"
date: "Washington University in St. Louis"
output:
  pdf_document: default
  html_document: default
---

# Age-Related Differences in Motivational Integration and Cognitive Control (Supplement)
This is an analysis of subject task performance in the aging motivation study, in which we examine age-related differences in how individuals integrate the motivational value of monetary and liquid studies, and whether and how this integrated motivational value interacts with cognitive control. In the study, subjects perform a cued task-switching paradigm, where they have classify a letter (vowel/consonant) or digit (odd/even). During the baseline runs, they don't receive any feedback and are told to respond "as quickly and accurate as possible." During the incentive runs, they receive a drop of liquid (2 mL) to indicate successful attainment of monetary reward in a single trial. Each subject performs 3 incentive runs in which they must respond accurately and faster than a criterion RT to earn monetary reward. Liquid feedback (blocked) served as reinforcement and signaled successful attainment of monetary reward. Criterion RT is calculated on subject performance during the baseline run (30%).

All relevant experimental scripts, subject data, and data analyses located in the online repository in Open Science Framework: https://osf.io/3mztb/

# Loading relevant packages
```{r packages, message=FALSE}
library(ggplot2)
library(gridExtra)
library(dplyr)
library(tidyr)
library(broom)
library(lme4)
library(lmerTest)
library(sjPlot)
library(sjstats)
library(pander)
library(effsize)
source("summarySEwithin2.R")
library(RColorBrewer)
```

# Specify colors
```{r colors}
display.brewer.pal(n = 8, name = 'Set2')
brewer.pal(n = 8, name = "Set2")
colors.OAYA<-c("#66C2A5","#FC8D62")
```

# Path directories of data input/output
```{r directories}
# data.path<-paste0("/Users/debbieyee/Box/CCPLab_Liquid_Studies_ARCHIVE/",
#                   "2018_MotivationAging/Study1_OA_Reinforcement/SubjectData/",
#                   "TrimmedData/OAYA_LiqPos_RewardData.csv")
# data.path.base<-paste0("/Users/debbieyee/Box/CCPLab_Liquid_Studies_ARCHIVE/",
#                   "2018_MotivationAging/Study1_OA_Reinforcement/SubjectData/",
#                   "TrimmedData/OAYA_LiqPos_BaselineData.csv")
# data.path.selfreport<-paste0("/Users/debbieyee/Box/CCPLab_Liquid_Studies_ARCHIVE/",
#                        "2018_MotivationAging/Study1_OA_Reinforcement/SubjectData/Redcap/",
#                        "OAYA_selfreport.csv")
# runkey.path<-paste0("/Users/debbieyee/Box/CCPLab_Liquid_Studies_ARCHIVE/",
#                     "2018_MotivationAging/Study1_OA_Reinforcement/SubjectData/",
#                     "TrimmedData/OAYA_LiqPos_runkey.csv")
# figure.path<-paste0("/Users/debbieyee/Box/CCPLab_Liquid_Studies_ARCHIVE/",
#                     "2018_MotivationAging/MotivationAging_Analyses/Figures")

# data directories
data.path<-"/Users/debbieyee/Documents/Manuscripts/2018/MotivationAging/Data/OAYA_LiqPos_RewardData.csv"
data.path.base<-"/Users/debbieyee/Documents/Manuscripts/2018/MotivationAging/Data/OAYA_LiqPos_BaselineData.csv"
data.path.selfreport<-"/Users/debbieyee/Documents/Manuscripts/2018/MotivationAging/Data/OAYA_selfreport.csv"
runkey.path<-"/Users/debbieyee/Documents/Manuscripts/2018/MotivationAging/Data/OAYA_LiqPos_runkey.csv"
figure.path<-"/Users/debbieyee/Documents/Manuscripts/2018/MotivationAging/Figures/"
```

# Format data for analysis
```{r data format}
# Read in the data
data<-read.csv(data.path,header = TRUE) %>% select(-X) 
data.base<-read.csv(data.path.base, header = TRUE) %>% select(-X)
runkey<-read.csv(runkey.path, header = TRUE) %>% filter(include=="yes")

# Formatting incentive data
incentive<- data %>% inner_join(y = runkey, by = c("subID","block","group"))  %>%
  mutate(subRewarded=(RT<critRT & ACC==1)*1,
         ERR=ifelse(ACC==0,1,0), 
         condition="incentive",
         block=factor(block, levels=c(7,8,9), labels=c(1,2,3)),
         money=factor(rewType, levels=c("Reward1","Reward2","Reward4"), labels=c("$","$$","$$$$")),
         moneyCode=factor(rewType, levels=c("Reward1","Reward2","Reward4"), labels=c(-1,0,1)),
         moneyweight=factor(rewType, levels=c("Reward1","Reward2","Reward4"), labels=c(.25,.50,1)),
         liqCode=factor(liquid, levels=c("saltwater","neutral","juice"), labels=c(-1,0,1)),
         liqCodeJvN=factor(liquid, levels=c("saltwater","neutral","juice"), labels=c(0,-1,1)),
         liqCodeSvN=factor(liquid, levels=c("saltwater","neutral","juice"), labels=c(-1,1,0)),
         groupCode=factor(group, levels=c("YA","OA"), labels=c(0,1)),
         blockCode=factor(block, levels=c(1,2,3), labels=c(-1,0,1)))
incentive$moneyCode<-as.numeric(levels(incentive$moneyCode)[incentive$moneyCode])
incentive$moneyweight<-as.numeric(levels(incentive$moneyweight)[incentive$moneyweight])
incentive$liqCode<-as.numeric(levels(incentive$liqCode)[incentive$liqCode])
incentive$liqCodeJvN<-as.numeric(levels(incentive$liqCodeJvN)[incentive$liqCodeJvN])
incentive$liqCodeSvN<-as.numeric(levels(incentive$liqCodeSvN)[incentive$liqCodeSvN])
incentive$groupCode<-as.numeric(levels(incentive$groupCode)[incentive$groupCode])
incentive$blockCode<-as.numeric(levels(incentive$blockCode)[incentive$blockCode])
```

# Calculate monetary earnings per group
```{r monetary earnings}
# Calculate average monetary earnings per group
test<-incentive %>% filter(group=="YA") %>% group_by(subID) %>% 
  summarise(totalreward=sum(moneyearned))
mean(test$totalreward)
sd(test$totalreward)
test<-incentive %>% filter(group=="OA") %>% group_by(subID) %>% 
  summarise(totalreward=sum(moneyearned))
mean(test$totalreward)
sd(test$totalreward)
```

# Summarise/consolidate incentive data
```{r summarise data}
# summarise means by subject
groupRT.means = incentive %>% group_by(subID, group) %>%
  filter(!is.na(subRewarded), ACC==1) %>% filter(!is.na(subRewarded), ACC==1) %>%
  summarise(n=n(),meanRT = mean(RT))
group.means = incentive %>% group_by(subID, group) %>% filter(!is.na(subRewarded)) %>%
  summarise(n=n(), meanRR = mean(subRewarded), seRR= sd(subRewarded)/sqrt(length(subRewarded)),
            meanACC = mean(ACC), meanERR = mean(ERR))

# summarise means by monetary reward only
rewRT.means = incentive %>% group_by(subID, money, group) %>%
  filter(!is.na(subRewarded), ACC==1) %>% filter(!is.na(subRewarded), ACC==1) %>%
  summarise(n=n(),meanRT = mean(RT))
rew.means = incentive %>% group_by(subID,money, group) %>% filter(!is.na(subRewarded)) %>%
  summarise(n=n(), meanRR = mean(subRewarded), meanACC = mean(ACC), meanERR = mean(ERR))

# summarise means by liquid incentive type only
liqRT.means = incentive %>% group_by(subID, liquid, group, block) %>% 
  filter(!is.na(subRewarded), ACC==1) %>% 
  summarise(meanRT = mean(RT))
liq.means=incentive %>% group_by(subID, liquid, group, block) %>% filter(!is.na(subRewarded)) %>%
  summarise(n=n(), meanRR = mean(subRewarded), meanACC = mean(ACC), meanERR = mean(ERR))

# summarise the means of the incentive data for each subject, grouped by condition
incentive9RT.means <- incentive %>% group_by(subID, liquid, money, group, block) %>%
  filter(!is.na(subRewarded), ACC==1) %>% summarise(n=n(), meanRT = mean(RT)) %>%
  mutate(moneycode = as.numeric(as.character(factor(money,levels=c("$","$$","$$$$"),
                                                    labels=c(-1,0,1)))),
         liqcode = as.numeric(as.character(factor(liquid,levels=c("saltwater","neutral","juice"),
                                                  labels=c(-1,0,1))))) %>%
  ungroup(subID) %>% mutate(subID=as.factor(subID))
incentive9.means = incentive %>% group_by(subID, liquid, money, group, block) %>% 
  filter(!is.na(subRewarded)) %>%
  summarise(n = n(), meanRR = mean(subRewarded), meanACC = mean(ACC), meanERR = mean(ERR)) %>%
  mutate(moneycode = as.numeric(as.character(factor(money,levels=c("$","$$","$$$$"),
                                                    labels=c(-1,0,1)))),
         liqcode = as.numeric(as.character(factor(liquid,levels=c("saltwater","neutral","juice"),
                                                  labels=c(-1,0,1))))) %>%
  ungroup(subID) %>% mutate(subID=as.factor(subID))
```

\newpage
# Monetary Rewards Improve Cognitive Task Performance for Both Older and Younger Adults
## Plot: histogram of reward rate by age group
```{r}
RR.sum=summarySE2(data=group.means, measurevar = "meanRR", groupvars = c("group"))
pandoc.table(RR.sum)
p.RR.0<-ggplot() + 
  geom_bar(data = RR.sum, aes(x=group, y=meanRR, fill=group), 
           color="black",stat="identity") + 
  geom_errorbar(data = RR.sum, 
                mapping=aes(x=group, y=meanRR,
                            ymin=meanRR-se, ymax=meanRR+se), 
                stat="identity", width=0.2) +
  geom_point(data = group.means, aes(x=group, y=meanRR),
             stat="identity", position=position_jitter(w=.3), alpha=0.5) +
  geom_hline(yintercept = .30, linetype="dashed") +
  geom_hline(yintercept = .35) +
  geom_hline(yintercept = .25) +
  annotate("rect", xmin = 0, xmax = 3, ymin = .25, ymax = .35,
        alpha = .2) + 
  xlab("Age Group") + ylab("Reward Rate") +
  coord_cartesian(ylim=c(0,.85)) +
  scale_fill_brewer(palette="Set2") +
  theme(#plot.title=element_text(size=22,face="bold", vjust=2),
        axis.title=element_text(size=12,face = "bold"),
        axis.text=element_text(size=14),
        legend.position="none",
        strip.text.x = element_text(size = 12))
p.RR.0
```

## Binomial test
```{r}
binom.test(x = 86, n = 288, p = .05, alternative = "two.sided")
```

\newpage
## Plot: RT between baseline and incentive blocks.
```{r}
# Merge baseline and incentive data
cond.RT.base <- data.base %>% 
  mutate(block=0) %>%
  select(subID, group, Trial, RT, ACC, condition, block, taskswitch=taskSwitch) %>%
  filter(ACC==1) %>%
  mutate(RT_log = log(RT))
cond.RT.rew <- incentive %>% 
  select(subID, group, Trial, RT, ACC, condition, block, taskswitch) %>%
  filter(ACC==1) %>%
  mutate(RT_log = log(RT))
cond.RT<-rbind(cond.RT.base,cond.RT.rew) 

RT.sum=summarySEwithin2(data=cond.RT, measurevar = "RT", withinvars = c("condition"),
                        betweenvars = c("group"), idvar = "subID")
pandoc.table(RT.sum)
p.RT.0<-ggplot(data = RT.sum, aes(x=group, y = RT, fill=condition)) +
  geom_bar(position=position_dodge(width=0.8), color="black",
           stat="identity", width=0.8) + 
  geom_errorbar(position=position_dodge(width=0.8),
                aes(ymin=RT-se, ymax=RT+se), width=.2) +
  xlab("Age Group") + ylab("Response Time (ms)") +
  labs(fill = "Block") +
  coord_cartesian(ylim=c(500,1000)) +
  scale_fill_brewer(palette="Set1") +
  theme(#plot.title=element_text(size=22,face="bold", vjust=2),
    axis.title=element_text(size=12,face = "bold"),
    axis.text=element_text(size=14),
    legend.position=c(.85,.85),
    legend.box.background = element_rect(colour = "black"),
    strip.text.x = element_text(size = 12))
p.RT.0
```

## RT by baseline vs incentive block for each age group 
```{r}
# consolidating RT data between baseline and incentive
cond.RT<-cond.RT %>%
  mutate(groupCode=factor(group, levels=c("YA","OA"), labels=c(0,1)),
         conditionCode=factor(condition, levels=c("baseline","incentive"), labels=c(1,0)))
cond.RT$groupCode<-as.numeric(levels(cond.RT$groupCode)[cond.RT$groupCode])
cond.RT$conditionCode<-as.numeric(levels(cond.RT$conditionCode)[cond.RT$conditionCode])

# summarizing to have one datapoint per subject per condition.
cond.RT.sum <- cond.RT %>% group_by(subID,group,condition) %>%
  summarise(meanRT = mean(RT), meanRT_log = mean(RT_log))

# OA baseline vs incentive block
# run paired t-test 
t.test(x = subset(cond.RT.sum, group=="OA" & condition=="baseline")$meanRT_log,
       y = subset(cond.RT.sum, group=="OA" & condition=="incentive")$meanRT_log,
       paired = TRUE)
# calculate cohen's d
cohen.d(subset(cond.RT.sum, group=="OA" & condition=="incentive")$meanRT_log,
        subset(cond.RT.sum, group=="OA" & condition=="baseline")$meanRT_log,
        na.rm = TRUE, pooled = TRUE, paired = TRUE, hedges.correction = FALSE)

# YA baseline vs incentive block
t.test(x = subset(cond.RT.sum, group=="YA" & condition=="baseline")$meanRT_log,
       y = subset(cond.RT.sum, group=="YA" & condition=="incentive")$meanRT_log,
       paired = TRUE)
cohen.d(subset(cond.RT.sum, group=="YA" & condition=="incentive")$meanRT_log,
        subset(cond.RT.sum, group=="YA" & condition=="baseline")$meanRT_log,
        na.rm = TRUE, pooled = TRUE, paired = TRUE, hedges.correction = FALSE)
```

\newpage
## Plot: accuracy between baseline and incentive blocks
```{r}
# Merge baseline and incentive data
cond.ACC.base <- data.base %>% mutate(block=0) %>%
  select(subID, group, Trial, RT, ACC, condition, block, taskswitch=taskSwitch)
cond.ACC.rew <- incentive %>% select(subID, group, Trial, RT, ACC, condition, block,taskswitch)
cond.ACC<-rbind(cond.ACC.base,cond.ACC.rew) 

ACC.sum=summarySEwithin2(data=cond.ACC, measurevar = "ACC", withinvars = c("condition"),
                        betweenvars = c("group"), idvar = "block")
p.ACC.0<-ggplot(data = ACC.sum, aes(x=group, y = ACC, fill=condition)) +
  geom_bar(position=position_dodge(width=0.8), color="black",
           stat="identity", width = 0.8) + 
  geom_errorbar(position=position_dodge(width=0.8),
                aes(ymin=ACC-se, ymax=ACC+se), width=.2) +
  xlab("Age Group") + ylab("Accuracy") +
  labs(fill = "Block") +
  coord_cartesian(ylim=c(.7,1)) +
  scale_fill_brewer(palette="Set1") +
  theme(#plot.title=element_text(size=22,face="bold", vjust=2),
    axis.title=element_text(size=12,face = "bold"),
    axis.text=element_text(size=14),
    legend.position=c(.85,.85),
    legend.box.background = element_rect(colour = "black"),
    strip.text.x = element_text(size = 12))
p.ACC.0
```

## Accuracy by baseline vs incentive block for each age group 
```{r}
# consolidating accuracy data between baseline and incentive
cond.ACC<-cond.ACC %>%
  mutate(groupCode=factor(group, levels=c("YA","OA"), labels=c(0,1)),
         conditionCode=factor(condition, levels=c("baseline","incentive"), labels=c(1,0)))
cond.ACC$groupCode<-as.numeric(levels(cond.ACC$groupCode)[cond.ACC$groupCode])
cond.ACC$conditionCode<-as.numeric(levels(cond.ACC$conditionCode)[cond.ACC$conditionCode])

# summarizing to have one datapoint per subject per condition.
cond.ACC.sum <- cond.ACC %>% group_by(subID,group,condition) %>%
  summarise(meanACC = mean(ACC))

# OA baseline vs incentive block
# t-test
t.test(x = subset(cond.ACC.sum, group=="OA" & condition=="baseline")$meanACC,
       y = subset(cond.ACC.sum, group=="OA" & condition=="incentive")$meanACC,
       paired = TRUE)
# calculate cohen's d
cohen.d(subset(cond.ACC.sum, group=="OA" & condition=="incentive")$meanACC,
        subset(cond.ACC.sum, group=="OA" & condition=="baseline")$meanACC,
        na.rm = TRUE, pooled = TRUE, paired = TRUE, hedges.correction = FALSE)

# YA baseline vs incentive block
# t-test
t.test(x = subset(cond.ACC.sum, group=="YA" & condition=="baseline")$meanACC,
       y = subset(cond.ACC.sum, group=="YA" & condition=="incentive")$meanACC,
       paired = TRUE)
# calculate cohen's d
cohen.d(subset(cond.ACC.sum, group=="YA" & condition=="incentive")$meanACC,
        subset(cond.ACC.sum, group=="YA" & condition=="baseline")$meanACC,
        na.rm = TRUE, pooled = TRUE, paired = TRUE, hedges.correction = FALSE)

```


\newpage
## Plot: RT Switch costs between baseline and incentive blocks
```{r}
cond.RT.switch <- cond.RT %>%
  group_by(subID,group,condition,taskswitch) %>%
  filter(Trial!=1, ACC==1) %>%
  summarise(meanRT = mean(RT)) %>%
  spread(key = taskswitch, value = meanRT) %>%
  rename(taskrepeat="0",taskswitch="1") %>%
  mutate(switchcost = taskswitch-taskrepeat)

SW.sum=summarySEwithin2(data=cond.RT.switch, measurevar = "switchcost", 
                        withinvars = c("condition"), betweenvars = c("group"), 
                        idvar = "subID")
pandoc.table(SW.sum)
p.SW.1<-ggplot(data = SW.sum, aes(x=group, y = switchcost, fill=condition)) +
  geom_bar(position=position_dodge(width=0.8), color="black",
           stat="identity", width=0.8) + 
  geom_errorbar(position=position_dodge(width=0.8),
                aes(ymin=switchcost-se, ymax=switchcost+se), width=.2) +
  xlab("Age Group") + ylab("RT switch cost (ms)") +
  labs(fill = "Block") +
  #coord_cartesian(ylim=c(500,1000)) +
  scale_fill_brewer(palette="Set1") +
  theme(#plot.title=element_text(size=22,face="bold", vjust=2),
    axis.title=element_text(size=12,face = "bold"),
    axis.text=element_text(size=14),
    legend.position=c(.85,.85),
    legend.box.background = element_rect(colour = "black"),
    strip.text.x = element_text(size = 12))
p.SW.1
```

## RT switch costs analysis
```{r}
# OA baseline vs incentive block
# t-test
t.test(x = subset(cond.RT.switch, group=="OA" & condition=="baseline")$switchcost,
       y = subset(cond.RT.switch, group=="OA" & condition=="incentive")$switchcost,
       paired = TRUE)
# calculate cohen's d
cohen.d(subset(cond.RT.switch, group=="OA" & condition=="incentive")$switchcost,
        subset(cond.RT.switch, group=="OA" & condition=="baseline")$switchcost,
        na.rm = TRUE, pooled = TRUE, paired = TRUE, hedges.correction = FALSE)

# YA baseline vs incentive block
# t-test
t.test(x = subset(cond.RT.switch, group=="YA" & condition=="baseline")$switchcost,
       y = subset(cond.RT.switch, group=="YA" & condition=="incentive")$switchcost,
       paired = TRUE)
# calculate cohen's d
cohen.d(subset(cond.RT.switch, group=="YA" & condition=="incentive")$switchcost,
        subset(cond.RT.switch, group=="YA" & condition=="baseline")$switchcost,
        na.rm = TRUE, pooled = TRUE, paired = TRUE, hedges.correction = FALSE)
```


\newpage
## Plot: Accuracy Switch costs between baseline and incentive blocks
```{r}
cond.ACC.switch <- cond.ACC %>%
  group_by(subID,group,condition,taskswitch) %>%
  filter(Trial!=1) %>%
  summarise(meanACC = mean(ACC)) %>%
  spread(key = taskswitch, value = meanACC) %>%
  rename(taskrepeat="0",taskswitch="1") %>%
  mutate(switchcost = taskswitch-taskrepeat)

SW.sum=summarySEwithin2(data=cond.ACC.switch, measurevar = "switchcost", 
                        withinvars = c("condition"), betweenvars = c("group"), 
                        idvar = "subID")
pandoc.table(SW.sum)
p.SW.2<-ggplot(data = SW.sum, aes(x=group, y = switchcost, fill=condition)) +
  geom_bar(position=position_dodge(width=0.8), color="black",
           stat="identity", width=0.8) + 
  geom_errorbar(position=position_dodge(width=0.8),
                aes(ymin=switchcost-se, ymax=switchcost+se), width=.2) +
  xlab("Age Group") + ylab("Accuracy switch cost (ms)") +
  labs(fill = "Block") +
  #coord_cartesian(ylim=c(500,1000)) +
  scale_fill_brewer(palette="Set1") +
  theme(#plot.title=element_text(size=22,face="bold", vjust=2),
    axis.title=element_text(size=12,face = "bold"),
    axis.text=element_text(size=14),
    legend.position=c(.85,.85),
    legend.box.background = element_rect(colour = "black"),
    strip.text.x = element_text(size = 12))
p.SW.2
```

## Accuracy switch costs analysis
```{r}
# OA baseline vs incentive block
# t-test
t.test(x = subset(cond.ACC.switch, group=="OA" & condition=="baseline")$switchcost,
       y = subset(cond.ACC.switch, group=="OA" & condition=="incentive")$switchcost,
       paired = TRUE)
# calculate cohen's d
cohen.d(subset(cond.ACC.switch, group=="OA" & condition=="incentive")$switchcost,
        subset(cond.ACC.switch, group=="OA" & condition=="baseline")$switchcost,
        na.rm = TRUE, pooled = TRUE, paired = TRUE, hedges.correction = FALSE)

# YA baseline vs incentive block
# t-test
t.test(x = subset(cond.ACC.switch, group=="YA" & condition=="baseline")$switchcost,
       y = subset(cond.ACC.switch, group=="YA" & condition=="incentive")$switchcost,
       paired = TRUE)
# calculate cohen's d
cohen.d(subset(cond.ACC.switch, group=="YA" & condition=="incentive")$switchcost,
        subset(cond.ACC.switch, group=="YA" & condition=="baseline")$switchcost,
        na.rm = TRUE, pooled = TRUE, paired = TRUE, hedges.correction = FALSE)
```


## Generalized Linear Mixed Models: Reward Rate Effects by Monetary Reward and Age
```{r}
# Monetary Reward Effect
m.RR.money<-glmer(formula = subRewarded ~ moneyCode * groupCode + (1+moneyCode|subID),
          data = incentive, family = binomial)
summary(m.RR.money)
# Calculating Cohen's f effect sizes for specific variables
sjstats::cohens_f(m.RR.money)

# YA
m.RR.money.YA <-glmer(formula = subRewarded ~ moneyCode + (1+moneyCode|subID),
          data = subset(incentive,groupCode==0), family = binomial)
summary(m.RR.money.YA)
# Calculating Cohen's f effect sizes for specific variables
sjstats::cohens_f(m.RR.money.YA)

# OA
m.RR.money.OA <-glmer(formula = subRewarded ~ moneyCode + (1+moneyCode|subID),
          data = subset(incentive,group=="OA"), family = binomial)
summary(m.RR.money.OA)
# Calculating Cohen's f effect sizes for specific variables
sjstats::cohens_f(m.RR.money.OA)

```


\newpage
## Plot: barplot of reward rate by monetary reward and age group
```{r}
RR.sum=summarySEwithin2(data=rew.means, measurevar = "meanRR", withinvars = c("money"),
                        betweenvars = c("group"), idvar = "subID")
pandoc.table(RR.sum)
p.RR.1<-ggplot(RR.sum, aes(x=money, y=meanRR,fill=group)) +
  geom_bar(position=position_dodge(width=0.8), color="black", 
           stat="identity", width=0.8) +
  geom_errorbar(position=position_dodge(width=0.8), 
                aes(ymin=meanRR-se, ymax=meanRR+se), width=.2) +
  facet_grid(.~group) +
  geom_hline(yintercept = .30, linetype="dashed") +
  xlab("Monetary Reward") + ylab("Reward Rate") +
  #ggtitle("Task Performance Across Money") +
  coord_cartesian(ylim=c(.3,.8)) +
  #scale_fill_discrete(name="Monetary Reward") +
  scale_fill_brewer(palette="Set2") +
  theme(#plot.title=element_text(size=22,face="bold", vjust=2),
        axis.title=element_text(size=12,face = "bold"),
        axis.text=element_text(size=14),
        legend.position="none",
        strip.text.x = element_text(size = 12))
p.RR.1
```

\newpage
## Plot: RT by age group and money
```{r}
RT.sum=summarySEwithin2(data=rewRT.means, measurevar = "meanRT", withinvars = c("money"),
                        betweenvars = c("group"), idvar = "subID")
pandoc.table(RT.sum)
p.RT.1<-ggplot(RT.sum, aes(x=money, y=meanRT, fill=group)) +
  geom_bar(position=position_dodge(width=0.8), color="black", 
           stat="identity", width=0.8) +
  geom_errorbar(position=position_dodge(width=0.8), 
                aes(ymin=meanRT-se, ymax=meanRT+se), width=.2) +
  facet_grid(.~group) +
  xlab("Monetary Reward") + ylab("Response Time (ms)") +
  #ggtitle("Task Performance Across Money") +
  coord_cartesian(ylim=c(400,850)) +
  #scale_fill_discrete(name="Monetary Reward") +
  scale_fill_brewer(palette="Set2") +
  theme(#plot.title=element_text(size=22,face="bold", vjust=2),
        axis.title=element_text(size=12,face = "bold"),
        axis.text=element_text(size=14),
        legend.position="none",
        strip.text.x = element_text(size = 12))
p.RT.1
```

\newpage
## General Linear Mixed Effects Models of RT by Monetary Reward and Age Group
```{r}
incentiveRT<- incentive %>% filter(ACC==1) 

# Monetary Reward x Group Effects
m.RT.money <-lmer(formula = RT ~ moneyCode * groupCode + (1+moneyCode|subID),
          data = incentiveRT, REML = FALSE)
summary(m.RT.money)
# Calculating Cohen's f effect sizes for specific variables
sjstats::cohens_f(m.RT.money)

# YA
m.RT.money.YA <-lmer(formula = RT ~ moneyCode + (1+moneyCode|subID),
          data = subset(incentiveRT,group=="YA"), REML = FALSE)
summary(m.RT.money.YA)
# Calculating Cohen's f effect sizes for specific variables
sjstats::cohens_f(m.RT.money.YA)

# OA
m.RT.money.OA <-lmer(formula = RT ~ moneyCode + (1+moneyCode|subID),
          data = subset(incentive,group=="OA"), REML = FALSE)
summary(m.RT.money.OA)
# Calculating Cohen's f effect sizes for specific variables
sjstats::cohens_f(m.RT.money.OA)
```

\newpage
## Plot: Accuracy by age group and money
```{r}
ACC.sum=summarySEwithin2(data=rew.means, measurevar = "meanACC", withinvars = c("money"),
                        betweenvars = c("group"), idvar = "subID")
pandoc.table(ACC.sum)
p.ACC.1<-ggplot(ACC.sum, aes(x=money, y=meanACC, fill=group)) +
  geom_bar(position=position_dodge(width=0.8), color="black", 
           stat="identity", width=0.8) +
  geom_errorbar(position=position_dodge(width=0.8), 
                aes(ymin=meanACC-se, ymax=meanACC+se), width=.2) +
  facet_grid(.~group) +
  xlab("Monetary Reward") + ylab("Accuracy") +
  #ggtitle("Task Performance Across Money") +
  coord_cartesian(ylim=c(.65,.9)) +
  #scale_fill_discrete(name="Monetary Reward") +
  scale_fill_brewer(palette="Set2") +
  theme(#plot.title=element_text(size=22,face="bold", vjust=2),
        axis.title=element_text(size=12,face = "bold"),
        axis.text=element_text(size=14),
        legend.position="none",
        strip.text.x = element_text(size = 12))
p.ACC.1
```

\newpage
## Generalized Linear Mixed Effects Models of Accuracy by Monetary Reward and Age Group
```{r}
# Monetary Reward 
m.ACC.money <-glmer(formula = ACC ~ moneyCode * groupCode + (1+moneyCode|subID),
          data = incentive, family="binomial")
summary(m.ACC.money)
# Calculating Cohen's f effect sizes for specific variables
sjstats::cohens_f(m.ACC.money)

# YA
m.ACC.money.YA <-glmer(formula = ACC ~ moneyCode + (1+moneyCode|subID),
          data = subset(incentive,group=="YA"), family="binomial")
summary(m.ACC.money.YA)
# Calculating Cohen's f effect sizes for specific variables
sjstats::cohens_f(m.ACC.money.YA)

# OA
m.ACC.money.OA <-glmer(formula = ACC ~ moneyCode + (1+moneyCode|subID),
          data = subset(incentive,group=="OA"), family="binomial")
summary(m.ACC.money.OA)
# Calculating Cohen's f effect sizes for specific variables
sjstats::cohens_f(m.ACC.money.OA)
```

\newpage
# Combined RT-Accuracy Plot
```{r}
RTACC.sum<-full_join(x = RT.sum, y = ACC.sum, by=c("group","money","N"))
p.RTACC.1<-ggplot(data = RTACC.sum, aes(x = meanRT, y = meanACC, color=group)) + 
  geom_errorbar(aes(ymin=meanACC-se.y, ymax=meanACC+se.y), width=0, size=.75) +
  geom_errorbarh(aes(xmin=meanRT-se.x, xmax=meanRT+se.x), height=0, size=.75) +
  geom_point(aes(shape=money), size=1.5, color="black") +
  xlab("Response Time (ms)") + ylab("Accuracy") +
  coord_cartesian(xlim=c(500,800), ylim=c(.75,.9)) +
  scale_color_brewer(palette="Set2") +
  scale_fill_brewer(palette = "Set2") +
  theme(#plot.title=element_text(size=22,face="bold", vjust=2),
        axis.title=element_text(size=12,face = "bold"),
        axis.text=element_text(size=14),
        #legend.position="none",
        strip.text.x = element_text(size = 12))
p.RTACC.1
```


\newpage
# Transition Effects From Baseline to Incentive Blocks
## Plot: Transition between last 20 trials of baseline and first 20 trials of first incentive block.
```{r}
transition.base <- data.base %>% select(subID, group, Trial, RT, ACC, condition) %>%
  filter(Trial>=77) %>%
  mutate(Trial=Trial-97)
transition.reward <- incentive %>% filter(block==3 & Trial<=20) %>%
  select(subID, group, Trial, RT, ACC) %>%
  mutate(condition="incentive")
transition=rbind(transition.base,transition.reward)
transition <- transition %>% arrange(subID, condition, Trial) %>%
  group_by(subID) %>% 
  mutate(RT_zscore = scale(RT),
         ACC=as.numeric(ACC),
         groupCode=factor(group, levels=c("YA","OA"), labels=c(0,1)),
         conditionCode=factor(condition, levels=c("baseline","incentive"), labels=c(1,0))) 
transition$groupCode<-as.numeric(levels(transition$groupCode)[transition$groupCode])
transition$conditionCode<-as.numeric(levels(transition$conditionCode)[transition$conditionCode])
ix_NA<-which(transition$ACC==0)
transition$RT[ix_NA]<-""

trans.sum<-summarySEwithin2(data = transition, measurevar = "RT_zscore", betweenvars = "group",
                            withinvars = c("Trial","condition"), idvar = "subID", na.rm = TRUE)
trans.sum <- trans.sum  %>% arrange(group,Trial) %>%
  unite("group_cond", c("group","condition"), sep="_", remove = FALSE)
trans.sum$Trial<-as.numeric(levels(trans.sum$Trial)[trans.sum$Trial])

# Plotting z-scored RT
p.trans.1<-ggplot(data = trans.sum, mapping = aes(x = Trial, y = RT_zscore, shape=group_cond)) +
  geom_point(aes(color=group),size=3) +
  geom_smooth(method="lm", aes(group=group_cond), color="black", alpha=.3) +
  facet_grid(group~.) +
  coord_cartesian( ylim=c(-.9,.9)) +
  scale_color_brewer(palette="Set2") +
  scale_fill_brewer(palette = "Set2") +
  xlab("Trial Number") + ylab("Response Time (z-scored)") +
  labs(shape = "Block by Age Group", color = "Age Group") +
  theme(#plot.title=element_text(size=22,face="bold", vjust=2),
        axis.title=element_text(size=12,face="bold"),
        axis.text=element_text(size=14),
        #legend.position="none",
        #legend.title=element_text(),
        strip.text.x = element_text(size = 10))
p.trans.1
```

\newpage
## GLM: RT by trial, condition, and age group
Transition between last 20 trials of baseline and first 20 trials of first incentive block.
```{r}
# GLM on zscored RT
m.trans <-lmer(formula = RT_zscore ~ Trial * conditionCode * groupCode + (1|subID),
          data = transition)
summary(m.trans)
# Calculating Cohen's f effect sizes for specific variables
sjstats::cohens_f(m.trans)

# YA only
m.trans.YA <-lmer(formula = RT_zscore ~ Trial * conditionCode + (1|subID),
          data = subset(transition, group=="YA"))
summary(m.trans.YA)
# Calculating Cohen's f effect sizes for specific variables
sjstats::cohens_f(m.trans.YA)

# OA only
m.trans.OA <-lmer(formula = RT_zscore ~ Trial * conditionCode + (1|subID),
          data = subset(transition, group=="OA"))
summary(m.trans.OA)
# Calculating Cohen's f effect sizes for specific variables
sjstats::cohens_f(m.trans.OA)

# OA baseline
m.trans.OA.base <-lmer(formula = RT_zscore ~ Trial + (1|subID),
          data = subset(transition, group=="OA" & condition=="baseline"))
summary(m.trans.OA.base)
# Calculating Cohen's f effect sizes for specific variables
sjstats::cohens_f(m.trans.OA.base)

# OA incentive
m.trans.OA.incentive <-lmer(formula = RT_zscore ~ Trial + (1|subID),
          data = subset(transition, group=="OA" & condition=="incentive"))
summary(m.trans.OA.incentive)
# Calculating Cohen's f effect sizes for specific variables
sjstats::cohens_f(m.trans.OA.incentive)
```

## Plot: Transition of Accuracy between baseline and incentive block
```{r}
trans.sum<-summarySEwithin2(data = transition, measurevar = "ACC", betweenvars = "group",
                            withinvars = c("Trial","condition"), idvar = "subID", na.rm = TRUE)
trans.sum <- trans.sum  %>% arrange(group,Trial) %>%
  unite("group_cond", c("group","condition"), sep="_", remove = FALSE)
trans.sum$Trial<-as.numeric(levels(trans.sum$Trial)[trans.sum$Trial])

# Plotting Accuracy
p.trans.2<-ggplot(data = trans.sum, mapping = aes(x = Trial, y = ACC, shape=group_cond)) +
  geom_point(aes(color=group),size=3) +
  geom_smooth(method="lm", aes(group=group_cond), color="black", alpha=.3) +
  facet_grid(group~.) +
  coord_cartesian( ylim=c(0.6,1)) +
  scale_color_brewer(palette="Set2") +
  scale_fill_brewer(palette = "Set2") +
  xlab("Trial Number") + ylab("Accuracy") +
  labs(shape = "Block by Age Group", color = "Age Group") +
  theme(#plot.title=element_text(size=22,face="bold", vjust=2),
        axis.title=element_text(size=12,face="bold"),
        axis.text=element_text(size=14),
        #legend.position="none",
        #legend.title=element_text(),
        strip.text.x = element_text(size = 10))
p.trans.2
```

## GLM: Accuracy by trial, condition, and age group
Transition between last 20 trials of baseline and first 20 trials of first incentive block.
```{r}
# GLM on zscored ACC
m.trans.ACC <-glmer(formula = ACC ~ Trial * conditionCode * groupCode + (1|subID),
          data = transition, family="binomial")
summary(m.trans.ACC)
# Calculating Cohen's f effect sizes for specific variables
sjstats::cohens_f(m.trans.ACC)

# YA only
m.trans.ACC.YA <-glmer(formula = ACC ~ Trial * conditionCode + (1|subID),
          data = subset(transition, group=="YA"), family="binomial")
summary(m.trans.ACC.YA)
# Calculating Cohen's f effect sizes for specific variables
sjstats::cohens_f(m.trans.ACC.YA)

# OA only
m.trans.ACC.OA <-glmer(formula = ACC ~ Trial * conditionCode + (1|subID),
          data = subset(transition, group=="OA"), family="binomial")
summary(m.trans.ACC.OA)
# Calculating Cohen's f effect sizes for specific variables
sjstats::cohens_f(m.trans.ACC.OA)

# OA only baseline
m.trans.ACC.OA.baseline <-glmer(formula = ACC ~ Trial + (1|subID),
          data = subset(transition, group=="OA" & condition=="baseline"), family="binomial")
summary(m.trans.ACC.OA.baseline)
# Calculating Cohen's f effect sizes for specific variables
sjstats::cohens_f(m.trans.ACC.OA.baseline)
# OA only incentive
m.trans.ACC.OA.incentive <-glmer(formula = ACC ~ Trial + (1|subID),
          data = subset(transition, group=="OA" & condition=="incentive"), family="binomial")
summary(m.trans.ACC.OA.incentive)
# Calculating Cohen's f effect sizes for specific variables
sjstats::cohens_f(m.trans.ACC.OA.incentive)
```

\newpage
# Integration of Primary and Secondary Motivational Incentives in Older and Younger Adults
## Plot: Reward rate by monetary reward, liquid, and age group
```{r}
RR.sum=summarySEwithin2(data=incentive9.means, measurevar = "meanRR",
                        withinvars = c("money","liquid"), betweenvars = c("group"),
                        idvar = "subID")
pandoc.table(RR.sum)
# first plot
p.RR.2<-ggplot(RR.sum, aes(x=liquid, y=meanRR, fill=money)) +
  geom_bar(position=position_dodge(width=0.8), color="black", 
           stat="identity", width=0.8) +
  geom_errorbar(position=position_dodge(width=0.8), 
                aes(ymin=meanRR-se, ymax=meanRR+se), width=.2) +
  xlab("Liquid Feedback") + ylab("Reward Rate") +
  labs(fill = "Money") +
  facet_grid(.~group) +
  geom_hline(yintercept = .30, linetype="dashed") +
  scale_fill_brewer(palette="Set1") +
  coord_cartesian(ylim=c(.3,.8)) +
  #scale_fill_discrete(name="Monetary Reward") +
  theme(#plot.title=element_text(size=22,face="bold", vjust=2),
        axis.title=element_text(size=12,face = "bold"),
        axis.text=element_text(size=14),
        legend.position="right",
        strip.text.x = element_text(size = 12))
p.RR.2
```

\newpage
## Analysis: Reward Rate by money, liquid, and age group
```{r}
# Monetary Reward 
m.RR.mot9<-glmer(formula = subRewarded ~ moneyCode * liqCode * groupCode + 
                   (1+moneyCode+liqCode|subID),
          data = incentive, family="binomial")
summary(m.RR.mot9)
# Calculating Cohen's f effect sizes for specific variables
sjstats::cohens_f(m.RR.mot9)

# YA
m.RR.mot9.YA <-glmer(formula = subRewarded ~ moneyCode * liqCode + 
                       (1+moneyCode+liqCode|subID),
          data = subset(incentive,group=="YA"), family="binomial")
summary(m.RR.mot9.YA)
# Calculating Cohen's f effect sizes for specific variables
sjstats::cohens_f(m.RR.mot9.YA)
# Juice vs Neutral
m.RR.mot9.YA.JvN <-glmer(formula = subRewarded ~ moneyCode * liqCode + 
                           (1+moneyCode+liqCode|subID),
          data = subset(incentive,group=="YA" && liquid!="saltwater"), 
          family="binomial")
summary(m.RR.mot9.YA.JvN)
# Calculating Cohen's f effect sizes for specific variables
sjstats::cohens_f(m.RR.mot9.YA.JvN)
# Saltwater vs Neutral
m.RR.mot9.YA.SvN <-glmer(formula = subRewarded ~ moneyCode * liqCode + 
                           (1+moneyCode+liqCode|subID),
          data = subset(incentive,group=="YA" & liquid!="juice"), 
          family="binomial")
summary(m.RR.mot9.YA.SvN)
# Calculating Cohen's f effect sizes for specific variables
sjstats::cohens_f(m.RR.mot9.YA.SvN)

# OA
m.RR.mot9.OA <-glmer(formula = subRewarded ~ moneyCode * liqCode + 
                       (1+moneyCode+liqCode|subID),
          data = subset(incentive,group=="OA"), family="binomial")
summary(m.RR.mot9.OA)
# Calculating Cohen's f effect sizes for specific variables
sjstats::cohens_f(m.RR.mot9.OA)
```

## Plot: mean reward rate by block, money, and age group
```{r}
RR.sum=summarySEwithin2(data=incentive9.means, measurevar = "meanRR",
                        withinvars = c("block","liquid"), betweenvars = c("group"),
                        idvar = "subID")
pandoc.table(RR.sum)
# first plot
p.RR.3<-ggplot(RR.sum, aes(x=block, y=meanRR, fill=liquid)) +
  geom_bar(position=position_dodge(width=0.8), color="black", 
           stat="identity", width=0.8) +
  geom_errorbar(position=position_dodge(width=0.8), 
                aes(ymin=meanRR-se, ymax=meanRR+se), width=.2) +
  xlab("Incentive Block Number") + ylab("Reward Rate") +
  labs(fill = "Liquid") +
  facet_grid(.~group) +
  geom_hline(yintercept = .30, linetype="dashed") +
  scale_fill_brewer(palette="Set1") +
  coord_cartesian(ylim=c(.3,.8)) +
  theme(#plot.title=element_text(size=22,face="bold", vjust=2),
        axis.title=element_text(size=12,face = "bold"),
        axis.text=element_text(size=14),
        legend.position="right",
        strip.text.x = element_text(size = 12))
p.RR.3
```

\newpage
## Analysis: RR by liquid, block, and age group
```{r}
# Monetary Reward 
m.RR.motblock <-glmer(formula = subRewarded ~ liqCode * blockCode * groupCode + 
                        moneyCode + (1+moneyCode+liqCode|subID),
          data = incentive, family="binomial")
summary(m.RR.motblock)
# Calculating Cohen's f effect sizes for specific variables
sjstats::cohens_f(m.RR.motblock)

# OA
m.RR.motblock.OA <-glmer(formula = subRewarded ~ liqCode * blockCode + moneyCode +
                           (1+moneyCode+liqCode|subID),
          data = subset(incentive,group=="OA"), family="binomial")
summary(m.RR.motblock.OA)
# Calculating Cohen's f effect sizes for specific variables
sjstats::cohens_f(m.RR.motblock.OA)

# Money & Liquid Effects in Block 1
m.RR.motblock.OA.b1 <-glmer(formula = subRewarded ~ liqCode + moneyCode + 
                              (1+moneyCode+liqCode|subID),
          data = subset(incentive,group=="OA" & block==1), family="binomial")
summary(m.RR.motblock.OA.b1)
# Calculating Cohen's f effect sizes for specific variables
sjstats::cohens_f(m.RR.motblock.OA.b1)
# Money & Effects in Block 3
m.RR.motblock.OA.b3 <-glmer(formula = subRewarded ~ liqCode + moneyCode + 
                              (1+moneyCode+liqCode|subID),
          data = subset(incentive,group=="OA" & block==3), family="binomial")
summary(m.RR.motblock.OA.b3)
# Calculating Cohen's f effect sizes for specific variables
sjstats::cohens_f(m.RR.motblock.OA.b3)

# YA
m.RR.motblock.YA <-glmer(formula = subRewarded ~ liqCode * blockCode + moneyCode +
                           (1+moneyCode+liqCode|subID),
          data = subset(incentive,group=="YA"), family="binomial")
summary(m.RR.motblock.YA)
# Calculating Cohen's f effect sizes for specific variables
sjstats::cohens_f(m.RR.motblock.YA)
# block 1
m.RR.motblock.YA.b1 <-glmer(formula = subRewarded ~ liqCode + moneyCode + 
                              (1+moneyCode+liqCode|subID),
          data = subset(incentive,group=="YA" & block==1), family="binomial")
summary(m.RR.motblock.YA.b1)
# Calculating Cohen's f effect sizes for specific variables
sjstats::cohens_f(m.RR.motblock.YA.b1)
# block 3
m.RR.motblock.YA.b3 <-glmer(formula = subRewarded ~ liqCode + moneyCode + 
                              (1+moneyCode+liqCode|subID),
          data = subset(incentive,group=="YA" & block==3), family="binomial")
summary(m.RR.motblock.YA.b3)
# Calculating Cohen's f effect sizes for specific variables
sjstats::cohens_f(m.RR.motblock.YA.b3)
```

## Analysis comparing OA performance in block 3 vs YA performance in block 1
```{r}
# OA block 3 vs YA block 1
t.test(x = subset(liq.means, group=="OA" & block==3)$meanRR,
       y = subset(liq.means, group=="YA" & block==1)$meanRR,
       paired=FALSE)
cohen.d(subset(liq.means, group=="OA" & block==3)$meanRR,
        subset(liq.means, group=="YA" & block==1)$meanRR,
        na.rm = TRUE, pooled = TRUE, paired = FALSE, hedges.correction = FALSE)
```

\newpage
# Reinforcement Effects Model: Trialwise Estimated Values  
```{r trialwise-estimate-values}
# Define constant parameters  
L = 0.5
val_init = 0.5

# Loop over subjects and add estimated value based on previously rewarded trial
SUBJECTS = unique(incentive$subID)
#SUBJECTS = 1
incentive$value_est=999
for (subj.id in SUBJECTS) {
  # filter data for subject
  tmp.data<-filter(incentive,subID==subj.id)
  
  # remove values_subj vector 
  if (exists("values_subj")) {rm(values_subj)}
  if (exists("values_subj_param")) {rm(values_subj_param)}
  
  # loop over blocks (1,2,3)
  BLOCKS=as.numeric(unique(tmp.data$block))
  for (b in BLOCKS) {
    # filter data for block
    tmp.data.block<-filter(tmp.data,block==b)
    # loop over trials within each block
    values = vector(mode = "numeric", length=96)
    values_param = vector(mode = "numeric", length=96)
    for (t in tmp.data.block$Trial) {
      # calculate estimated value per trial based on reinforcement/previous reward
      # non-parametric version: based only previous reward only
      # parametric version: based on previous reward & monetary value
      if (t==1) {
        values[t]=val_init
        values_param[t]=val_init
      } else {
        # nonparametric
        values[t]=((1-L)*values[t-1]) + L*as.numeric(tmp.data.block$subRewarded[t-1])
        # parametric
        w = tmp.data.block$moneyweight[t-1]
        values_param[t]=((1-L)*values_param[t-1]) + 
          L*as.numeric(w*tmp.data.block$subRewarded[t-1])
      } 
      
    } # end for loop over trials
    
    # concatenate the values from blocks for each subject
    if (exists("values_subj")) {values_subj<-c(values_subj,values)
    } else {values_subj<-values}
    
    # concatenate the values from blocks for each subject: parametric
    if (exists("values_subj_param")) {values_subj_param<-c(values_subj_param,values_param)
    } else {values_subj_param<-values_param}
    
  } # end for loop over blocks

  # identify indices for where in data frame to enter value estimates
  ix<-which(incentive$subID==subj.id)
  # add value estimates to the data frame
  incentive[ix,"value_est"]=round(values_subj,4)
  incentive[ix,"value_est_param"]=round(values_subj_param,4)
  
} # end for loop over subjects 

```

# Plotting Group Averaged Value Estimates 
```{r, fig.width=8, fig.height=11}
data.group.value.estimates <- incentive %>% group_by(Trial,group,liquid,block) %>%
  summarise(n=n(),value_est_mean = mean(value_est), 
            value_est_param_mean = mean(value_est_param)) %>%
  arrange(block,liquid,group,Trial)
levels(data.group.value.estimates$block)[levels(data.group.value.estimates$block)=="1"] <- "Block 1"
levels(data.group.value.estimates$block)[levels(data.group.value.estimates$block)=="2"] <- "Block 2"
levels(data.group.value.estimates$block)[levels(data.group.value.estimates$block)=="3"] <- "Block 3"
names(data.group.value.estimates)[3]<-"Liquid"

# Plotting group value estimates
p.val.1<-ggplot(data = data.group.value.estimates,
                mapping=aes(x=Trial,y=value_est_mean, 
                            color=Liquid, shape=Liquid)) +
  geom_point(alpha=0.75) + 
  geom_smooth(method="lm", se=FALSE) +
  coord_cartesian(ylim=c(0,1), xlim=c(1,96)) + 
  facet_grid(group~block) + 
  xlab("Trial Number") + ylab("Value Estimate") + 
  #labs(shape = "Liquid") +
  scale_color_brewer(palette="Set1") +
  theme(#plot.title=element_text(size=22,face="bold", vjust=2),
        axis.title=element_text(size=12,face = "bold"),
        axis.text=element_text(size=12),
        #legend.position="none",
        strip.text.x = element_text(size = 12),
        strip.text.y = element_text(size = 12),
        panel.spacing = unit(.75, "lines"))
p.val.1
```

\newpage 
# Generalized Linear Mixed Model
Logistic regression of Estimated Reward Value and Experimental Conditions (money, liquid, blocks), as well as group (older adults vs younger adults).
```{r}
# Reward Rate predicted by estimated value (reinforcement)
m.val.1 <-glmer(formula = subRewarded ~ value_est + (1|subID),
          data = incentive, family=binomial)
summary(m.val.1)

# money, liquid, age group effects, including estimated value 
m.val.2 <-glmer(formula = subRewarded ~ moneyCode*liqCode + value_est*blockCode*groupCode +
                  value_est:liqCode +
                  (1+moneyCode+liqCode|subID),
          data = incentive, family=binomial)
summary(m.val.2)

# younger adults value estimate
m.val.2a <-glmer(formula = subRewarded ~ liqCode*moneyCode + blockCode*value_est +
                   value_est:liqCode + (1+moneyCode+liqCode|subID),
          data = filter(incentive,group=="YA" & liquid!="neutral"), family=binomial)
summary(m.val.2a)

# older adults value estimate
m.val.2b <-glmer(formula = subRewarded ~ liqCode*moneyCode + blockCode*value_est + 
                   value_est:liqCode + (1+moneyCode+liqCode|subID),
          data = filter(incentive,group=="OA"), family=binomial)
summary(m.val.2b)
```

\newpage
# Self-Report Ratings
## Formatting Data
```{r}
data.selfreport<-read.csv(data.path.selfreport) %>%
  filter(include=="yes")
```

## Plot of Self-Report Liking Ratings per Liquid
```{r}
# formatting the liking data from wide to long form
data.liking<-data.selfreport %>% 
  select(subID, group, Juice=juice_like, Neutral=neut_like, Saltwater=salt_like) %>%
  gather(key = liquid, value = rating, Juice:Saltwater, factor_key=TRUE) %>%
  mutate(liqCode = factor(liquid, levels = c("Saltwater","Neutral","Juice"), labels=c(-1,0,1)),
         groupCode = factor(group, levels=c("YA","OA"), labels=c(0,1)))
data.liking$liqCode<-as.numeric(levels(data.liking$liqCode)[data.liking$liqCode])
data.liking$groupCode<-as.numeric(levels(data.liking$groupCode)[data.liking$groupCode])  

selfreport.sum<-summarySEwithin2(data = data.liking, measurevar = "rating",
                                 withinvars = c("liquid"), betweenvars = "group",
                                 idvar = "subID")
p.rating.1<-ggplot(data = selfreport.sum, aes(x = liquid, y = rating, fill=group)) +
  geom_bar(stat = "identity", color="black") +
  geom_errorbar(mapping = aes(ymin=rating-se, ymax=rating+se), width=.2) +
  xlab("Liquid") + ylab("Liking Rating") +
  scale_x_discrete(labels=c("juice_like" = "Juice", 
                            "neut_like" = "Neutral",
                            "salt_like" = "Saltwater")) +
  facet_grid(.~group) + 
  scale_fill_brewer(palette = "Set2") +
  #coord_cartesian(ylim=c(1,7)) +
  theme(#plot.title=element_text(size=22,face="bold", vjust=2),
    axis.title=element_text(size=12,face = "bold"),
    axis.text=element_text(size=14),
    legend.position="none",
    strip.text.x = element_text(size = 12))
p.rating.1
```

\newpage
## Stats on Liking Ratings
```{r}
m.selfreport.1<-lmer(formula = rating ~ liqCode*groupCode + (1|subID), data = data.liking)
summary(m.selfreport.1)
# OA
m.selfreport.1.OA<-lmer(formula = rating ~ liqCode + (1|subID), 
                        data = subset(data.liking, group=="OA"))
summary(m.selfreport.1.OA)
# OA JvN
t.test(x = subset(data.liking, liquid=="Juice" & group=="OA")$rating,
       y = subset(data.liking, liquid=="Neutral" & group=="OA")$rating,
       paired = TRUE)

# OA NvS
t.test(x = subset(data.liking, liquid=="Neutral" & group=="OA")$rating,
       y = subset(data.liking, liquid=="Saltwater" & group=="OA")$rating,
       paired = TRUE)

# YA
m.selfreport.1.YA<-lmer(formula = rating ~ liqCode + (1|subID), 
                        data = subset(data.liking, group=="YA"))
summary(m.selfreport.1.YA)
# YA JvN
t.test(x = subset(data.liking, liquid=="Juice" & group=="YA")$rating,
       y = subset(data.liking, liquid=="Neutral" & group=="YA")$rating,
       paired = TRUE)
# YA NvS
t.test(x = subset(data.liking, liquid=="Neutral" & group=="YA")$rating,
       y = subset(data.liking, liquid=="Saltwater" & group=="YA")$rating,
       paired = TRUE)

# OA vs YA
# Juice
t.test(x = subset(data.liking, liquid=="Juice" & group=="OA")$rating,
       y = subset(data.liking, liquid=="Juice" & group=="YA")$rating)
# Neutral
t.test(x = subset(data.liking, liquid=="Neutral" & group=="OA")$rating,
       y = subset(data.liking, liquid=="Neutral" & group=="YA")$rating)
# Saltwater
t.test(x = subset(data.liking, liquid=="Saltwater" & group=="OA")$rating,
       y = subset(data.liking, liquid=="Saltwater" & group=="YA")$rating)
```

## Plot of Self-Report Intensity Ratings per Liquid
```{r}
# formatting the intensity data from wide to long form
data.intensity<-data.selfreport %>% 
  select(subID, group, Juice=juice_intense, Neutral=neut_intense, Saltwater=salt_intense) %>%
  gather(key = liquid, value = rating, Juice:Saltwater, factor_key=TRUE) %>%
  mutate(liqCode = factor(liquid, levels = c("Saltwater","Neutral","Juice"), labels=c(-1,0,1)),
         groupCode = factor(group, levels=c("YA","OA"), labels=c(0,1)))
data.intensity$liqCode<-as.numeric(levels(data.intensity$liqCode)[data.intensity$liqCode])
data.intensity$groupCode<-as.numeric(levels(data.intensity$groupCode)[data.intensity$groupCode])  


selfreport.sum<-summarySEwithin2(data = data.intensity, measurevar = "rating",
                                 withinvars = c("liquid"), betweenvars = "group",
                                 idvar = "subID")
p.rating.2<-ggplot(data = selfreport.sum, aes(x = liquid, y = rating, fill=group)) +
  geom_bar(stat = "identity", color="black") +
  geom_errorbar(mapping = aes(ymin=rating-se, ymax=rating+se), width=.2) +
  xlab("Liquid") + ylab("Intensity Rating") +
  scale_x_discrete(labels=c("juice_intense" = "Juice", 
                            "neut_intense" = "Neutral",
                            "salt_intense" = "Saltwater")) +
  facet_grid(.~group) + 
  scale_fill_brewer(palette = "Set2") +
  #coord_cartesian(ylim=c(1,7)) +
  theme(#plot.title=element_text(size=22,face="bold", vjust=2),
    axis.title=element_text(size=12,face = "bold"),
    axis.text=element_text(size=14),
    legend.position="none",
    strip.text.x = element_text(size = 12))
p.rating.2
```

\newpage
## Stats on Intensity Ratings
```{r}
m.selfreport.2<-lmer(formula = rating ~ liqCode*groupCode + (1|subID), 
                     data = data.intensity)
summary(m.selfreport.2)
# OA
m.selfreport.2.OA<-lmer(formula = rating ~ liqCode + (1|subID), 
                        data = subset(data.intensity, group=="OA"))
summary(m.selfreport.2.OA)
# OA JvN
t.test(x = subset(data.intensity, liquid=="Juice" & group=="OA")$rating,
       y = subset(data.intensity, liquid=="Neutral" & group=="OA")$rating,
       paired = TRUE)

# OA NvS
t.test(x = subset(data.intensity, liquid=="Saltwater" & group=="OA")$rating,
       y = subset(data.intensity, liquid=="Neutral" & group=="OA")$rating,
       paired = TRUE)

# YA
m.selfreport.2.YA<-lmer(formula = rating ~ liqCode + (1|subID), 
                        data = subset(data.intensity, group=="YA"))
summary(m.selfreport.2.YA)
# YA JvN
t.test(x = subset(data.intensity, liquid=="Juice" & group=="YA")$rating,
       y = subset(data.intensity, liquid=="Neutral" & group=="YA")$rating,
       paired = TRUE)
# YA NvS
t.test(x = subset(data.intensity, liquid=="Saltwater" & group=="YA")$rating,
       y = subset(data.intensity, liquid=="Neutral" & group=="YA")$rating,
       paired = TRUE)

# OA vs YA
# Juice
t.test(x = subset(data.intensity, liquid=="Juice" & group=="OA")$rating,
       y = subset(data.intensity, liquid=="Juice" & group=="YA")$rating)
# Neutral
t.test(x = subset(data.intensity, liquid=="Neutral" & group=="OA")$rating,
       y = subset(data.intensity, liquid=="Neutral" & group=="YA")$rating)
# Saltwater
t.test(x = subset(data.intensity, liquid=="Saltwater" & group=="OA")$rating,
       y = subset(data.intensity, liquid=="Saltwater" & group=="YA")$rating)
```

\newpage
##  Plot of Self-Report Motivation Ratings per Trial Type
```{r}
# 9 motivation ratings
data.motive9<-data.selfreport %>% 
  select(subID, group, 
         Juice_1=juice1_motivation, Juice_2=juice2_motivation, Juice_4=juice4_motivation,
         Neutral_1=neut1_motivation, Neutral_2=neut2_motivation, Neutral_4=neut4_motivation,
         Saltwater_1=salt1_motivation, Saltwater_2=salt2_motivation, Saltwater_4=salt4_motivation) %>%
  gather(key = condition, value = rating, Juice_1:Saltwater_4, factor_key = TRUE) %>%
  separate(col = condition, into=c("liquid","moneyreward"), sep = "_") %>%
  mutate(liqCode = factor(liquid, levels = c("Saltwater","Neutral","Juice"), labels=c(-1,0,1)),
         rewCode = factor(moneyreward, levels = c(1,2,4), labels=c(-1,0,1)),
         groupCode = factor(group, levels=c("YA","OA"), labels=c(0,1)),
         money=factor(moneyreward, levels=c(1,2,4), labels=c("$","$$","$$$$")))  
data.motive9$liqCode<-as.numeric(levels(data.motive9$liqCode)[data.motive9$liqCode])
data.motive9$rewCode<-as.numeric(levels(data.motive9$rewCode)[data.motive9$rewCode])
data.motive9$groupCode<-as.numeric(levels(data.motive9$groupCode)[data.motive9$groupCode])  
data.motive9$subID<-as.factor(data.motive9$subID)

selfreport.sum<-summarySEwithin2(data = data.motive9, measurevar = "rating",
                                 withinvars = c("liquid","money"), betweenvars = "group",
                                 idvar = "subID")
p.rating.3<-ggplot(data = selfreport.sum, aes(x = liquid, y = rating, fill = money)) +
  geom_bar(position=position_dodge(), stat = "identity", color="black") +
  geom_errorbar(position=position_dodge(.9),
                mapping = aes(ymin=rating-se, ymax=rating+se), width=.2) +
  xlab("Liquid") + ylab("Motivation Rating") +
  scale_x_discrete(labels=c("juice_intense" = "Juice", 
                            "neut_intense" = "Neutral",
                            "salt_intense" = "Saltwater")) +
  facet_grid(.~group) + 
  scale_fill_brewer(palette = "Set1") +
  #coord_cartesian(ylim=c(1,7)) +
  theme(#plot.title=element_text(size=22,face="bold", vjust=2),
    axis.title=element_text(size=12,face = "bold"),
    axis.text=element_text(size=14),
    legend.position="right",
    strip.text.x = element_text(size = 12))
p.rating.3
```


\newpage
## Stats on Motivation Ratings by Trial Type
```{r}
m.selfreport.3<-lmer(formula = rating ~ liqCode*rewCode*groupCode + (1|subID), 
                     data = data.motive9)
summary(m.selfreport.3)
# OA
m.selfreport.3.OA<-lmer(formula = rating ~ liqCode*rewCode + (1|subID), 
                        data = subset(data.motive9, group=="OA"))
summary(m.selfreport.3.OA)
# OA JvN
m.selfreport.3.OA.JvN<-lmer(formula = rating ~ liqCode*rewCode + (1|subID),
                        data = subset(data.motive9, group=="OA" & liquid!="Saltwater"))
summary(m.selfreport.3.OA.JvN)
# OA NvS
m.selfreport.3.OA.NvS<-lmer(formula = rating ~ liqCode*rewCode + (1|subID),
                        data = subset(data.motive9, group=="OA" & liquid!="Juice"))
summary(m.selfreport.3.OA.NvS)

# YA
m.selfreport.3.YA<-lmer(formula = rating ~ liqCode*rewCode + (1|subID), 
                        data = subset(data.motive9, group=="YA"))
summary(m.selfreport.3.YA)
# YA JvN
m.selfreport.3.YA.JvN<-lmer(formula = rating ~ liqCode*rewCode + (1|subID),
                        data = subset(data.motive9, group=="YA" & liquid!="Saltwater"))
summary(m.selfreport.3.YA.JvN)
# YA NvS
m.selfreport.3.YA.NvS<-lmer(formula = rating ~ liqCode*rewCode + (1|subID),
                        data = subset(data.motive9, group=="YA" & liquid!="Juice"))
summary(m.selfreport.3.YA.NvS)

# OA vs YA
# Juice
m.selfreport.3.OAYA.Juice<-lmer(formula = rating ~ groupCode*rewCode + (1|subID), 
                        data = subset(data.motive9, liquid=="Juice"))
summary(m.selfreport.3.OAYA.Juice)
# Neutral
m.selfreport.3.OAYA.Neutral<-lmer(formula = rating ~ groupCode*rewCode + (1|subID), 
                        data = subset(data.motive9, liquid=="Neutral"))
summary(m.selfreport.3.OAYA.Neutral)
# Saltwater
m.selfreport.3.OAYA.Saltwater<-lmer(formula = rating ~ groupCode*rewCode + (1|subID), 
                        data = subset(data.motive9, liquid=="Saltwater"))
summary(m.selfreport.3.OAYA.Saltwater)
```

\newpage
## Comparing Motivation Ratings and Reward Rate
```{r}
incentive9.means.indiv <- incentive9.means %>%
  mutate(liquid = factor(liquid, levels = c("saltwater","neutral","juice"), 
                         labels=c("Saltwater","Neutral","Juice"))) %>%
  inner_join(y = data.motive9, by = c("subID","liquid","money","group")) %>%
  group_by(subID) %>%
  mutate(rating_zscore = scale(rating),
         meanRR_zscore = scale(meanRR))

p.rating.4<-ggplot(data = incentive9.means.indiv, 
                   aes(x = rating_zscore, y = meanRR_zscore, color=liquid, shape=liquid)) + 
  geom_point() +
  geom_smooth(method="lm", se = FALSE) +
  xlab("Motivation Rating") + ylab("Reward Rate") + 
  labs(shape = "Liquid", color="Liquid") +
  scale_color_brewer(palette="Set1") +
  facet_grid(group~money) + 
    theme(#plot.title=element_text(size=22,face="bold", vjust=2),
    axis.title=element_text(size=12,face = "bold"),
    axis.text=element_text(size=14),
    legend.position="right",
    strip.text.x = element_text(size = 12),
    strip.text.y = element_text(size = 12))
p.rating.4
```

```{r}
incentive9.means.indiv2<-filter(incentive9.means.indiv, is.na(rating)!=TRUE)
# OA Hierarchical Regression 
# Model 1
m.selfreport.4.OA.L1<-lmer(formula = meanRR ~ rewCode*liqCode + 
                             (1+rewCode|subID), 
                     data = subset(incentive9.means.indiv2, group=="OA"))
summary(m.selfreport.4.OA.L1)
# Model 2
m.selfreport.4.OA.L2<-lmer(formula = meanRR ~ rewCode*liqCode + rating + 
                             (1+rewCode|subID), 
                     data = subset(incentive9.means.indiv2, group=="OA"))
summary(m.selfreport.4.OA.L2)
# Model Comparison
anova(m.selfreport.4.OA.L1,m.selfreport.4.OA.L2)

# YA Hierarchical Regression
# Model 1
m.selfreport.4.YA.L1<-lmer(formula = meanRR ~ rewCode*liqCode + 
                             (1+rewCode|subID), 
                     data = subset(incentive9.means.indiv2, group=="YA"))
summary(m.selfreport.4.YA.L1)
# Model 2
m.selfreport.4.YA.L2<-lmer(formula = meanRR ~ rewCode*liqCode + rating + 
                             (1+rewCode|subID), 
                     data = subset(incentive9.means.indiv2, group=="YA"))
summary(m.selfreport.4.YA.L2)
# Model Comparison
anova(m.selfreport.4.YA.L1, m.selfreport.4.YA.L2)
```

# Manuscript Figures
```{r}
ms.path="/Users/debbieyee/Documents/Manuscripts/In Progress/Motivation Aging/Figures/"
ggsave(filename = "Figure2a_group.eps", plot = p.RR.0, 
       device=cairo_ps, fallback_resolution = 600,
       path = ms.path, width = 3, height = 6, scale = 1)
ggsave(filename = "Figure2b_RT.eps", plot = p.RT.0, device = "eps", 
       path = ms.path, width = 6, height = 6, scale = 1)
ggsave(filename = "Figure2c_ACC.eps", plot = p.ACC.0, device = "eps", 
       path = ms.path, width = 6, height = 6, scale = 1)
ggsave(filename = "Figure3_Transition.eps", plot = p.trans.1, 
       device = cairo_ps,
       path = ms.path, width = 12, height = 4, scale = 1)
ggsave(filename = "Figure4a_RR-mon-liq.eps", plot = p.RR.2, 
       device = "eps",
       path = ms.path, width = 8, height = 4, scale = 1)
ggsave(filename = "Figure4b_RR-mon-block.eps", plot = p.RR.3, 
       device = "eps",
       path = ms.path, width = 8, height = 4, scale = 1)
ggsave(filename = "Figure5_ValEst.eps", plot = p.val.1, 
       device = cairo_ps,
       path = ms.path, width = 10, height = 6, scale = 1)
ggsave(filename = "Figure6a_Liking.eps", plot = p.rating.1, 
       device = "eps",
       path = ms.path, width = 5.5, height = 5, scale = 1) 
ggsave(filename = "Figure6b_Intensity.eps", plot = p.rating.2, 
       device = "eps",
       path = ms.path, width = 5.5, height = 5, scale = 1) 
ggsave(filename = "Figure6c_Motivation.eps", plot = p.rating.4, 
       device = "eps",
       path = ms.path, width = 12, height = 6, scale = 1) 
```

